### 2018-01-04 Writeup/PERT_New.tex
Updated writeup and the readin functions for stratafication

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{color}
\usepackage{amssymb}
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{verbatim}
\usepackage{multirow}
\usepackage{framed}
\usepackage{natbib}
\usepackage{float, subfig}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{amsfonts}
\usepackage{listings}
\usepackage{amsthm}
\usepackage{grffile}
\usepackage{sidecap}
\usepackage{pbox}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

@@

\section{Introduction} \label{sec:intro}

@@

	In the planning stage of a project, decisions can be made to crash a certain set of activities in order to achieve the shortest project span. Here crashing an activity means accelerating its progress or compress its duration. In this paper, a discrete set of crashing options will be given to the decision makers, each with a fractional number which equals to the crashed duration divided by the original duration. One project can only be crashed once with one specific option. Each option will incur a certain cost as well and the total cost of crashing could not exceed the budget. Static crashing optimization problem is first researched in \cite{fulkerson1961network, kelley1961criticalpath}. If we assume a finite set of crashing options, the problem could be modeled as a mixed integer program. The static model can be extended to incorporate uncertainty of activity durations. Monte Carlo simulation methods are used to estimate the expected project span given distributions of activity lengths, since it is not really possible to provide an analytical expression of the true expected project span \cite{burt1971conditional,van1963letter}. Heuristics and simulation-based algorithms have been developed to solve the stochastic project crashing problem \cite{aghaie2009ant,ke2014genetic,kim2007heuristic}. Another approach to handle the uncertainty is the robust optimization method. In the robust optimization setting, the objective is to minimize the worst case project span within the uncertainty set. \textcolor{blue}{select a few papers about robust project crashing and describe what they did.}\\

@@

	We first formally describe the crashing optimization problem under stochastic disruptions. Given the limited number of disruption occurrence, the problem can be formulated as a stochastic mixed integer program and we will present the extensive formulation in Section~\ref{sec:formulation}. The large scale and the discrete non-convex nature of the extended formulation means it may not be solved efficiently to desirable tolerance level. In Section~\ref{sec:decomposition}, a branch-and-cut method based on Benders decomposition is developed to solve the crashing optimization problem with a disruption. We show such a decomposition method will solve the integer program to the exactness within finite number of iterations.\\

@@

	The experiment results are presented in Section~\ref{sec:results}, including the comparison between the quality of our solution and the solution obtained by solving a  crashing optimization problem with a deterministic disruption, and the computational performance of the decomposition method in Section~\ref{sec:decomposition}, compared to that of solving the extensive formulation. The experiment result shows \textcolor{blue}{(append summary of the experiment results here.)} We will conclude our paper with remarks on potential extensions of this model in Section~\ref{sec:conclusions}.

@@

	The deterministic project crashing optimization problem is widely researched since 1960s \cite{fulkerson1961network, kelley1961criticalpath}. Suppose the activity network is represented by a directed graph \(\mathcal{G} = (I,\mathcal{A})\), where the set of activities is denoted by \(I\) and their precedence relationship is characterized by \(\mathcal{A}\). Each element in set \(\mathcal{A}\) is a two dimensional vector \((i,k)\), which indicates that we have to finish activity \(i\) before starting activity \(k\), \(i,k \in I\).  The nominal length of each activity \(D_i\) is given, which means if there is no disruption, activity \(i\) will require \(D_i\) amount of time to finish. For each activity \(i \in I\), there is a finite set of crashing options \(j \in J_i\) and each of them will incur a cost of \(b_{ij}\). Applying crashing option \(j\) will decrease the activity length to \(1 - e_{ij}\) of its non-crashed length. We assume each activity can be crashed at most once and the total crashing cost could not be over a given budget \(B\). The deterministic project crashing problem could be formulated as follows:
	\begin{subequations} \label{prob:static}

@@

			\text{s.t.} \quad & t_N \geq t_i & \forall i \in I \label{cons:dotN}\\
			& t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) & \forall i \in I, (i,k) \in \mathcal{A} \label{cons:dott}\\
			& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B & \label{cons:doBudget}\\
			& \sum_{j \in J_i} x_{ij} \leq 1 & \forall i \in I\\
			& t_i \geq 0 & \forall i \in I\\
			& x_{ij} \in \{0,1\} & \forall i \in I, j \in J_i&

@@

	Based on this formulation, we can derive the stochastic optimization and the robust optimization models with reference to \textcolor{blue}{list the literature of stochastic/robust crashing optimization problems}. We omit these formulations in this paper since our uncertainty model is different from the literature listed above.\\

@@

	\begin{table}[H]
		\begin{tabular}{ l l l l }

@@

			\(F_i^\omega\) & \(\qquad\) & indicator whether activity \(i\) starts before disruption in realization \(\omega\), \(i \in I, \omega \in \Omega\);&\\

@@

		\end{tabular}
	\end{table}
	\noi The extensive formulation of the two-stage stochastic program is shown as Formulation~(\ref{prob:extensive}). Here \(M\) is a large number to enforce the logic relationships. In this problem, we are minimizing the expected project span by taking the sum of each scenario's project span weighted by the scenario probability. Variables \(F^\omega_i\) and \(G^\omega_i\) are used to identify whether activity \(i\) starts before or after the disruption time (in constraint (\ref{cons:F}) - (\ref{cons:FG})). This is important in our problem setting because the duration of each activity will depend on its temporal relationship to the disruption time, which is reflected in constraint (\ref{cons:duration}). For this duration constraint, the original expression of the duration of activity \(i\) is \((D_i + d_i^\omega G_i^\omega)(1 - \sum_{j \in J_i} e_{ij}x_{ij}^\omega)\). This contains a bilinear term \(G_i^\omega x_{ij}^\omega\), which can be linearized by introducing a binary variable \(S_{ij}^\omega\) and bounding it by constraints (\ref{cons:linearize1}) - (\ref{cons:linearize3}).\\

@@

	\begin{subequations} \label{prob:extensive}

@@

			\text{s.t.} \quad & t_N^\omega \geq t_i^\omega & \forall i \in I, \omega \in \Omega \\

@@

			& t_i^\omega \geq 0 & \forall i \in I, \omega \in \Omega\\
			& t_i \geq 0 & \forall i \in I\\
			& H^\omega - F_i^\omega M \leq t_i & \forall i \in I, \omega \in \Omega \label{cons:F}\\
			& H^\omega + G_i^\omega M \geq t_i & \forall i \in I, \omega \in \Omega \label{cons:G}\\
			& F_i^\omega + G_i^\omega = 1 & \forall i \in I, \omega \in \Omega \label{cons:FG}\\
			& t_i^\omega + (1 - F_i^\omega)M \geq t_i & \forall i \in I, \omega \in \Omega \label{cons:tF1}\\
			& t_i^\omega - (1 - F_i^\omega)M \leq t_i & \forall i \in I, \omega \in \Omega \label{cons:tF2}\\
			& x_{ij}^\omega + (1 - F_i^\omega)M \geq x_{ij} & \forall i \in I, j \in J_i, \omega \in \Omega \label{cons:xF1}\\
			& x_{ij}^\omega - (1 - F_i^\omega)M \leq x_{ij} & \forall i \in I, j \in J_i, \omega \in \Omega \label{cons:xF2}\\
			& t_k^\omega - t_i^\omega \geq D_i + d_i^\omega G_i^\omega -\sum_{j \in J_i} D_i e_{ij} x_{ij}^\omega - \sum_{j \in J_i} d_i^\omega e_{ij} S_{ij}^\omega & \forall i \in I, j \in J_i, \omega \in \Omega \label{cons:duration}\\
			& \sum_{j \in J_i} x_{ij}^\omega \leq 1 & \forall i \in I, \omega \in \Omega \label{cons:crashLim}\\
			& \sum_{i \in I}\sum_{j \in J_i} b_jx_{ij}^\omega \leq B & \forall \omega \in \Omega \label{cons:budget}\\
			& S_{ij}^\omega \leq G_i^\omega & \forall i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize1}\\
			& S_{ij}^\omega \leq x_{ij}^\omega & \forall i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize2}\\
			& S_{ij}^\omega \geq G_i^\omega + x_{ij}^\omega - 1 & \forall i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize3}\\
			& x_{ij}^\omega \in \{0,1\} & \forall i \in I, j \in J_i, \omega \in \Omega\\
			& F_i^\omega, G_i^\omega \in \{0,1\}. & \forall i \in I, \omega \in \Omega

@@

@@

		\item Formulation: master, sub
		\item Cut generation
		\item Branch and bound method
	Problem (\ref{prob:extensive}) is a two-sage stochastic mixed integer program with both binary (\(x\)) and continuous (\(t\)) state variables. A state variable here is a variable whose value is passed from the first stage to the second stage. Two-stage stochastic linear program could be solved nicely using Benders decomposition (\textcolor{blue}{cite Benders decomposition}). \\
	For our crashing optimization problem, we could separate the extensive formulation (\ref{prob:extensive}) into a master problem and a series of sub-problems as (\ref{prob:master}) and (\ref{prob:sub}). Constraint (\ref{cons:linearCuts}) are generated by solving the sub-problems iteratively for the optimal multipliers \(\pi\) and \(\lambda\). In a regular multi-cut Benders decomposition case, the sub problem is a convex optimization problem, usually a linear program. This means a finite number of constraints on \(\theta^\omega\) can fully characterize the function \(f^\omega(x,t)\). However, in this case \(f^\omega(x,t)\) is a mixed integer linear program. It is difficult to solve a stochastic mixed integer program with integer variables in the recourse problem because the linear cuts generated in the regular Benders decomposition could not characterize the recourse function exactly. \textcolor{blue}{cite literature about the stochastic integer programs}.
	\begin{subequations}
		\label{prob:master}
		(M) \quad \min \quad & p^0 t_N + \sum_{\omega \in \Omega} p^\omega \theta^\omega & \\
		\text{s.t.} \quad & t_N \geq t_i & \forall i \in I\\
		& t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) & \forall i \in I, (i,k) \in \mathcal{A}\\
		& \sum_{j \in J_i} x_{ij} \leq 1 & \forall i \in I\\
		& \theta^\omega \geq \sum_{i \in I} \pi_i^{\omega,k^\omega} t_i + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,k^\omega} x_{ij} + v^{\omega,k^\omega} & \forall \omega \in \Omega, k^\omega = 1,2, \dots \label{cons:linearCuts}\\
		& t_i \geq 0 & \forall i \in I\\
		& x_{ij} \in \{0,1\}. & \forall i \in I, j \in J_i&
	\begin{subequations}
		\label{prob:sub}
			(S^\omega) \quad f^\omega(\hat{x},\hat{t}) = \min \quad & t_N & \\
			\text{s.t.} \quad & t_N \geq t_i & \forall i \in I \\
			& H^\omega - F_i M \leq t_i & \forall i \in I \\
			& H^\omega + G_i M \geq t_i & \forall i \in I \\
			& F_i + G_i = 1 & \forall i \in I \\
			& t_i + (1-F_i) M \geq \hat{t}_i & \forall i \in I\\
			& t_i - (1-F_i) M \leq \hat{t}_i & \forall i \in I \\
			& x_{ij} + (1-F_i) \geq \hat{x}_{ij} & \forall i \in I, j \in J_i \\
			& x_{ij} - (1-F_i) \leq \hat{x}_{ij} & \forall i \in I, j \in J_i \\
			& t_k - t_i \geq D_i + d_i^\omega G_i -\sum_{j \in J_i} D_i e_{ij} x_{ij} - \sum_{j \in J_i} d_i^\omega e_{ij} S_{ij} & \forall i \in I, (i,k) \in \mathcal{A}\\
			&\sum_{i \in I} \sum_{j \in J_i} b_{ij} x_{ij} \leq B &\\
			& \sum_{j \in J_i} x_{ij} \leq 1 & \forall i \in I\\
			& S_{ij} \leq G_i & \forall i \in I, j \in J_i \\
			& S_{ij} \leq x_{ij} & \forall i \in I, j \in J_i\\
			& S_{ij} \geq G_i + x_{ij} - 1 & \forall i \in I, j \in J_i\\
			& t_i \geq 0 & \forall i \in I \\
			& x_{ij} \in \{0,1\}. & \forall i \in I, j \in J_i
	Recently Zou et al. \cite{zou2016nested} propose to generate Lagrangian cuts in the place of Benders cuts to solve multi-stage stochastic programs with only binary state variables. Their method keeps the structure of Benders decomposition and proves the tightness of Lagrangian cuts. To generate the Lagrangian multipliers, a local copy (\(\tau\) and \(z\)) of the state variable (\(\hat{t}\) and \(\hat{x}\)) is first created as in constraint (\ref{cons:local1}) and (\ref{cons:local2}) of formulation (\ref{prob:subLocal}). We can then relax the constraint (\ref{cons:local1}) and (\ref{cons:local2}) to create a Lagrangian dual problem (\ref{prob:LagDual}). The optimal solution  \(\pi^*\) and \(\lambda^*\) to the Lagrangian dual problem will be used in the Lagrangian cuts as in constraint (\ref{cons:linearCuts}). Problem (\ref{prob:LagDual}) can be solved by a subgradient method \textcolor{blue}{cite Fisher's tutorial for solving the Lagrangian Relaxation problem}.\\
	\begin{subequations}
		\label{prob:subLocal}
		(S^\omega_L) \quad \min \quad & t_N & \\
		\text{s.t.} \quad & t_N \geq t_i & \forall i \in I \label{cons:stN}\\
		& H^\omega - F_i M \leq t_i & \forall i \in I \\
		& H^\omega + G_i M \geq t_i & \forall i \in I \\
		& F_i + G_i = 1 & \forall i \in I \\
		& t_i + (1-F_i) M \geq \tau_i & \forall i \in I\\
		& t_i - (1-F_i) M \leq \tau_i & \forall i \in I \\
		& x_{ij} + (1-F_i) \geq z_{ij} & \forall i \in I, j \in J_i \\
		& x_{ij} - (1-F_i) \leq z_{ij} & \forall i \in I, j \in J_i \\
		& t_k - t_i \geq D_i + d_i^\omega G_i -\sum_{j \in J_i} D_i e_{ij} x_{ij} - \sum_{j \in J_i} d_i^\omega e_{ij} S_{ij} & \forall i \in I, (i,k) \in \mathcal{A}\\
		&\sum_{i \in I} \sum_{j \in J_i} b_{ij} x_{ij} \leq B &\\
		& \sum_{j \in J_i} x_{ij} \leq 1 & \forall i \in I\\
		& S_{ij} \leq G_i & \forall i \in I, j \in J_i \\
		& S_{ij} \leq x_{ij} & \forall i \in I, j \in J_i\\
		& S_{ij} \geq G_i + x_{ij} - 1 & \forall i \in I, j \in J_i \label{cons:s3}\\
		& z_{ij} = \hat{x}_{ij} & \forall i \in I, j \in J_i \label{cons:local1}\\
		& \tau_{i} = \hat{t}_{i} & \forall i \in I \label{cons:local2}\\
		& t_i \geq 0 & \forall i \in I \label{cons:tPos}\\
		& x_{ij} \in \{0,1\}. & \forall i \in I, j \in J_i\\
		& \tau_i \geq 0 & \forall i \in I \\
		& 0 \leq z_{ij} \leq 1 . & \forall i \in I, j \in J_i \label{cons:zRange}
	\begin{subequations}
		\label{prob:LagDual}
		(R^\omega) \quad \max_{\pi,\lambda} \min_{t,\tau,x,z} \quad & t_N + \sum_{i \in I} \pi_i(\tau_{i} - \hat{t}_i) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}(z_{ij} - \hat{x}_{ij}) & \\
		\text{s.t.} \quad & (\ref{cons:stN}) - (\ref{cons:s3})\text{ and } (\ref{cons:tPos}) - (\ref{cons:zRange}) \label{cons:X}
	The result from \cite{zou2016nested} could not be directly applied in our problem since our state variable contains both continuous variables \(t\) and binary variables \(x\). The Lagrangian cuts will only be a lower bound but the tightness could not be guaranteed. This means that if we carry out a cutting plane scheme using the Lagrangian cuts, solving the master problem (\ref{prob:master}) will only obtain a lower bound. \\
	One important observation to help with this issue is that if we can determine the temporal relationship between every activity and the disruption, it is always optimal to start the activity at its earliest possible time. For a feasible solution \((\hat{t},\hat{x})\), we define the shifted solution \((\tilde{t},\tilde{x})\) of \((\hat{t},\hat{x})\) as:
	\begin{definition}
		Shifted solution of a feasible solution \((\hat{t},\hat{x})\):
			\item \(\tilde{x}_{ij} = \hat{x}_{ij}\)
			\item For all activities which do not have a predecessor,\\
				\(\tilde{t}_i = 
				\begin{cases}
					H^\omega & \text{if temporal relationship information specifies } t_i \geq H^\omega\\
					0 & \text{otherwise.}
				\end{cases}
				\)
			\item For all other activities, \\
				\(\tilde{t}_i = 
				\begin{cases}
				\max \{H^\omega, \max_{i' \in I, i' \in I_i} \{\tilde{t}_{i'} + D_{i'}(1 - \sum_{j \in J_{i'}} e_{i'j}\tilde{x}_{i'j})\} \} & \text{if the temporal relationship}\\
				& \text{information specifies } t_i \geq H^\omega\\
				\max_{i' \in I, i' \in I_i} \{\tilde{t}_{i'} + D_{i'}(1 - \sum_{j \in J_{i'}} e_{i'j}\tilde{x}_{i'j})\} & \text{otherwise.}
				\end{cases}
				\)
	\end{definition}
	\noi We should notice that the temporal relationship should match the feasible solution. This is a natural result from solving problem~\ref{prob:subLocal} with temporal relationship information given. \\
	It is obvious to see the following statement is true because delaying an activity as soon as possible when the crashing decision is decided and temporal relationship information is revealed will not bring any benefit.
	\begin{corollary}
		For an optimal solution \((t^*,x^*)\) with correct temporal relationship information given for all activities, its shifted solution is also optimal.
	\end{corollary}
	\noi Now we will prove that the Lagrangian cuts generated by \cite{zou2016nested} is tight and valid at any shifted solution if temporal relationship information is given for all activities. This statement is very important because it provides an accurate evaluation at the optimal solution, which will lead to an algorithm which is able to solve problem~\ref{prob:extensive} to the exactness.
	\begin{proposition} \label{prop:convex}
		Suppose the set defined by constraint (\ref{cons:X}) is denoted by \(X\). For any shifted solution \((\tilde{t},\tilde{x})\) with temporal relationship information given for all \( i \in I\), 
		\[conv(X) \cap \{(\tau,z) \mid \tau_i = \tilde{t}_i, z_{ij} = \tilde{x}_{ij}, \tau_i, z_{ij} \in \mathbb{R}, \forall i \in I, j \in J_i \}  = \]
		\[conv(X \cap \{(\tau,z) \mid \tau_i = \tilde{t}_i, z_{ij} = \tilde{x}_{ij}, \tau_i, z_{ij} \in \mathbb{R}, \forall i \in I, j \in J_i \} )\]
	\end{proposition}
	\begin{proof}
		Suppose \((t^0, \tau^0, x^0, z^0) \in  conv(X) \cap \{(\tau,z) \mid \tau_i = \tilde{t}_i, z_{ij} = \tilde{x}_{ij}, \tau_i, z_{ij} \in \mathbb{R}, \forall i \in I, j \in J_i \} \). Then there exist a set of points in \(X\) indexed by \(k \in \mathcal{K}\) where \((t^0, \tau^0, x^0, z^0) = \sum_{k \in \mathcal{K}}\rho_{k} (t^k, \tau^k, x^k, z^k) \) and \(\rho_{k} \geq, \sum_{k \in \mathcal{K}} \rho_{k} = 1\). Since \(\tilde{x}_{ij} \in \{0,1\}, z_{ij}^k \in [0,1], \forall k \in \mathcal{K}\) and we have \(\sum_{k \in \mathcal{K}} \rho_{k} z^k_{ij} = z^0_{ij} = \tilde{x}_{ij}\), every \(z^k_{ij}\) can only take the same value as \(\tilde{x}_{ij} , \forall k \in \mathcal{K}\), which is an end point of \([0,1]\).\\
		\(z^k_{ij} = \tilde{x}_{ij}\) and temporal relationship information is given for all \(i \in I\), this means that the shifted solution \(\tilde{t}_i\) is the earliest possible starting time for activity \(i\), so \(\tau_i^k \geq \tilde{t}_i\). Similar to the previous statement about the relationship between \(z^k\) and \(\tilde{x}\), as \(\tilde{t}_i\) is taking an end point of the feasible set of \(\tau_i^k\) and \(\sum_{k \in \mathcal{K}} \rho_{k} \tau_i^k = \tilde{t}_i \), we have \(\tau_i^k = \tilde{t}_i,\ \forall k \in \mathcal{K}\). Combining the results above, 
		\[conv(X) \cap \{(\tau,z) \mid \tau_i = \tilde{t}_i, z_{ij} = \tilde{x}_{ij}, \tau_i, z_{ij} \in \mathbb{R}, \forall i \in I, j \in J_i \}  \subseteq \]
		\[conv(X \cap \{(\tau,z) \mid \tau_i = \tilde{t}_i, z_{ij} = \tilde{x}_{ij}, \tau_i, z_{ij} \in \mathbb{R}, \forall i \in I, j \in J_i \} )\]
		On the other hand, 
		\[conv(X) \cap \{(\tau,z) \mid \tau_i = \tilde{t}_i, z_{ij} = \tilde{x}_{ij}, \tau_i, z_{ij} \in \mathbb{R}, \forall i \in I, j \in J_i \}  \supseteq \]
		\[conv(X \cap \{(\tau,z) \mid \tau_i = \tilde{t}_i, z_{ij} = \tilde{x}_{ij}, \tau_i, z_{ij} \in \mathbb{R}, \forall i \in I, j \in J_i \} )\]

>>>>

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{color}
\usepackage{amssymb}
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{verbatim}
\usepackage{multirow}
\usepackage{framed}
\usepackage{natbib}
\usepackage{float, subfig}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{amsfonts}
\usepackage{listings}
\usepackage{amsthm}
\usepackage{grffile}
\usepackage{sidecap}
\usepackage{pbox}
\usepackage{algorithm}
\usepackage{longtable}
\usepackage[noend]{algpseudocode}

@@

\section{Introduction} \label{sec:introduction}

@@

	In the planning stage of a project, decisions can be made to crash a certain set of activities in order to achieve the shortest project span. Here crashing an activity means accelerating its progress or compress its duration. In this paper, a discrete set of crashing options will be given to the decision makers, each with a fractional number which equals to the crashed duration divided by the original duration. One project can only be crashed once with one specific option. Each option will incur a certain cost as well and the total cost of crashing could not exceed the budget. Static crashing optimization problem is first researched in \cite{fulkerson1961network, kelley1961criticalpath}. If we assume a finite set of crashing options, the problem could be modeled as a mixed integer program. The static model can be extended to incorporate uncertainty of activity durations. Monte Carlo simulation methods are used to estimate the expected project span given distributions of activity lengths, since it is not really possible to provide an analytical expression of the true expected project span \cite{burt1971conditional,van1963letter}. Heuristics and simulation-based algorithms have been developed to solve the stochastic project crashing problem \cite{aghaie2009ant,bowman1994stochastic,ke2014genetic,kim2007heuristic}. Another approach to handle the uncertainty is the robust optimization method. In the robust optimization setting, the objective is to minimize the worst case project span within the uncertainty set. It can be proved that an affinely adaptive recourse decision, although computationally tractable as it can be reformulated as a linear program or a second order conic program (SOCP), may lead to suboptimal solutions \cite{chen2008linear,cohen2007stochastic}. However, once the recourse decision rule is extended to a general form, it is only tractable to solve the robust optimization problem with hypercube uncertainty sets, which is a trivial case because the worst-case scenario in the uncertainty set is always the point where every activity takes the upper bound. \cite{wiesemann2012robust}. In recent years, distributionally robust optimization has been developed quickly in literature \cite{delage2010distributionally}. Ahipasaoglu et al. \cite{ahipasaoglu2016distributionally} propose a distributionally robust optimization scheme applied to PERT network, which reformulates the problem as a semidefinite program or a copositive program, depending on the description of uncertainty.\\

@@

	We first formally describe the crashing optimization problem under stochastic disruptions. Given the limited number of disruption occurrence, the problem can be formulated as a stochastic mixed integer program and we will present the extensive formulation in Section~\ref{sec:formulation}. If we assume continuous distributions for the disruption time and magnitude, sample average approximation (SAA) can be used to create a finite set of scenarios and approximate the original problem by a finite-sized optimization problem. We prove some important consistency and convergence properties of the SAA problem using independent and identically distributed samples and stratified samples in Section~\ref{sec:consistency}.\\

@@

	The large scale and the discrete non-convex nature of the SAA problem's extended formulation means it may not be solved efficiently to desirable tolerance level. In Section~\ref{sec:decomposition}, a branch-and-cut method based on Benders decomposition is developed to solve the crashing optimization problem with a disruption. We show such a decomposition method will solve the integer program to the exactness within finite number of iterations.\\
	The experiment results are presented in Section~\ref{sec:results}, including the comparison between the quality of our solution and the solution obtained by solving a  crashing optimization problem with a deterministic disruption, and the computational performance of the decomposition method in Section~\ref{sec:decomposition}, compared to that of solving the extensive formulation. We will conclude our paper with remarks on potential extensions of this model in Section~\ref{sec:conclusions}.

@@

	The deterministic project crashing optimization problem is widely researched since 1960s \cite{fulkerson1961network, kelley1961criticalpath}. Suppose the activity network is represented by a directed graph \(\mathcal{G} = (I,\mathcal{A})\), where the set of activities is denoted by \(I\) and their precedence relationship is characterized by \(\mathcal{A}\). The budget limit \(B\) and the nominal length of each activity \(D_i\) are given. For each activity \(i \in I\), there is a finite set of crashing options \(j \in J_i\) and each of them will incur a cost of \(b_{ij}\) while cutting down the nominal activity length to \(1 - e_{ij}\) of the nominal length.  We assume each activity could be crashed at most once and the problem could be formulated as follows. 
	\begin{subequations} \label{prob2:static}

@@

		\text{s.t.} \quad & t_N \geq t_i & \forall \,i \in I \\
		& t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) & \forall \,i \in I, (i,k) \in \mathcal{A}\\
		& \sum_{j \in J_i} x_{ij} \leq 1 & \forall \,i \in I\\
		& t_i \geq 0 & \forall \,i \in I\\
		& 0 \leq x_{ij} \leq 1 & \forall \,i \in I, j \in J_i&

@@

	Based on this formulation, we can derive the stochastic optimization and the robust optimization models with reference to the literature listed in Section~\ref{sec:introduction}. We omit these formulations in this paper since our uncertainty model is different from previous settings.\\

@@

	\begin{longtable}[H]{ l l l l }

@@

@@

	\end{longtable}
	\noi The extensive formulation of the two-stage stochastic program is shown as Formulation~(\ref{prob2:extensive}). Here \(M\) is a large number to enforce the logic relationships. In this problem, we are minimizing the expected project span by taking the sum of each scenario's project span weighted by the scenario probability. Variables \(G^\omega_i\) are used to identify whether activity \(i\) starts before or after the disruption time (in constraint (\ref{cons:F}) - (\ref{cons:G})). This is important in our problem setting because the duration of each activity will depend on its temporal relationship to the disruption time, which is reflected in constraint (\ref{cons:duration}). For this duration constraint, the original expression of the duration of activity \(i\) is \((D_i + d_i^\omega G_i^\omega)(1 - \sum_{j \in J_i} e_{ij}x_{ij}^\omega)\). This contains a bilinear term \(G_i^\omega x_{ij}^\omega\), which can be linearized by introducing a binary variable \(S_{ij}^\omega\) and bounding it by constraints (\ref{cons:linearize1}) - (\ref{cons:linearize3}).\\

@@

	\begin{subequations} \label{prob2:extensive}

@@

		\text{s.t.} \quad & t_N^\omega \geq t_i^\omega & \forall \,i \in I, \omega \in \Omega \\

@@

		& t_i^\omega \geq 0 & \forall \,i \in I, \omega \in \Omega\\
		& t_i \geq 0 & \forall \,i \in I\\
		& H^\omega - (1 - G_i^\omega) M \leq t_i & \forall \,i \in I, \omega \in \Omega \label{cons:F}\\
		& H^\omega + G_i^\omega M \geq t_i & \forall \,i \in I, \omega \in \Omega \label{cons:G}\\
		& t_i^\omega + G_i^\omega M \geq t_i & \forall \,i \in I, \omega \in \Omega \label{cons:tf1}\\
		& t_i^\omega - G_i^\omega M \leq t_i & \forall \,i \in I, \omega \in \Omega \label{cons:tf2}\\
		& x_{ij}^\omega + G_i^\omega \geq x_{ij} & \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:xf1}\\
		& x_{ij}^\omega - G_i^\omega \leq x_{ij} & \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:xf2}\\
		& t_k^\omega - t_i^\omega \geq D_i + d_i^\omega G_i^\omega -\sum_{j \in J_i} D_i e_{ij} x_{ij}^\omega - \sum_{j \in J_i} d_i^\omega e_{ij} S_{ij}^\omega & \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:duration}\\
		& \sum_{j \in J_i} x_{ij}^\omega \leq 1 & \forall \,i \in I, \omega \in \Omega \label{cons:crashLim}\\
		& \sum_{i \in I}\sum_{j \in J_i} b_jx_{ij}^\omega \leq B & \forall \,\omega \in \Omega \label{cons:budget}\\
		& S_{ij}^\omega \leq G_i^\omega & \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize1}\\
		& S_{ij}^\omega \leq x_{ij}^\omega & \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize2}\\
		& S_{ij}^\omega \geq G_i^\omega + x_{ij}^\omega - 1 & \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize3}\\
		& t_i \geq 0 & \forall\,i \in I \\
		& t_i^\omega \geq H^\omega G_i^\omega & \forall\, i \in I, \omega \in \Omega \\
		& 0 \leq x_{ij} \leq 1 & \forall \,i \in I, j \in J_i\\ 
		& 0 \leq x_{ij}^\omega \leq 1 & \forall \,i \in I, j \in J_i, \omega \in \Omega\\
		& G_i^\omega \in \{0,1\}. & \forall \,i \in I, \omega \in \Omega

@@

\section{Special Cases} \label{sec:examples}
	In this section we show a few examples to illustrate the properties of the project crashing problem under stochastic disruption displayed in Section~\ref{sec:formulation}. We will focus on simple network structures such as serial and parallel networks. We also display some general networks where those properties are (or not) applicable.
	\subsection{Serial Networks}
			\item Concavity of \(\mathbb{E}_d \left[ f(x,H,d) | H \right]\) in \(d\).
			\item The recourse function is a decreasing function in terms of remaining budget, given the same remaining task set.
			\item Not optimal to delay the start of activity \(i\) unless there is no investment before \(i\), given a fixed \(H\).
			\item Only optimal to delay to a possible disruption time.
		The first example we present for a serial network is to show that it might be optimal to delay the start of some activities. The reasons of such delay include:
		\begin{enumerate}
			\item Some activities might have a shorter length after disruption. It is beneficial to wait a short period of time to capture this advantage.
			\item Even if all possible disruption magnitudes are adverse, which means they will lengthen all activities, it is beneficial to delay an activity so that the crashing resource could be optimally applied according to the realization of disruption.
		\end{enumerate}
		Suppose we have a project with three activities in a serial network form. The activity 1 should be finished before the start of activity 2 and the activity 2 should be finished before the start of activity 3. The structure of the project is displayed as follows. We add two dummy activity ``S" and ``T" to represent the start and the end of the project. The total crashing budget is \(1\) and the allowed amount of crashing a single activity is between \(0\) and \(1\). 
		\begin{figure}[H]
			\centering
			\includegraphics[width=0.8\textwidth]{serial3}
			\caption{Example of a 3-activity project}
			\label{fig:serial3}
		\end{figure}
		\noi We can set up a nominal case with the length of activity 1, 2 and 3 as \(9\), \(10\) and \(7\). The probability of the disruption not occurring is 0.5. If a disruption occurs, it will occur at the time \(H = 9.1\). Suppose the disruption will change the length of activity 2 from \(10\) to \(3\) and not affect activity 3. We can see it is optimal to delay the start of activity 2 to \(t_2 = 9.1\), spend the entire budget to crash activity 3 if the disruption occurs, and spend the entire budget to crash activity 2 if the disruption does not occur. The expected total project span is 18.35. If we force the condition that the starting time of activities could not be delayed, we could not observe whether the disruption happens or not at the starting time of activity 2. There will be only one possible situation where three activities will have the duration as 9,10 and 7. All resources should be allocated to activity 2 and the total project span is 21, which is larger than the expected total project span if it is allowed to delay the starting time of some activities. The reason of such phenomenon is that a disruption may reduce some activities' durations. Delaying by a small amount will enable us to collect that reduction in time.\\
		Even if the disruption can only bring negative effect on the duration of activities, a.k.a. lengthening all activities after that, it is still beneficial to delay the start of some activities under some circumstances. This means a small delay of some activity may gain the information of disruption which is more valuable and potentially decreases the total project span. Such claim can be verified by the serial network described in the last paragraph, only changing some duration parameters in the following way. Suppose the nominal duration, the timing of possible disruption and the probability of a disruption occurring remain the same. If the disruption occurs, it will change the duration of activity 2 to 9.1 and that of activity 3 to 13. For this example, if no delay is allowed, the optimal decision is to allocate the entire budget to activity 2 and the expected total project span is 24. If we delay the starting time of the activity 2 to 9.1 so that the disruption can be observed before we commit resources to activity 2, the expected total project span is 23.4. 
	\subsection{Parallel Networks}
			\item Not optimal to delay when \(d_i \geq 0\).
	\subsection{Y Networks}
\section{Properties of the Sample Average Approximation Problem} \label{sec:consistency}
	\subsection{Cheat?}
	\subsection{Consistency and Convergence Results}
	\subsection{IID vs. Stratified Sampling}

@@

	Problem~\eqref{prob2:extensive} is a two-stage stochastic mixed integer program with binary variables in the second stage. 
\section{Experiment Results} \label{sec:results}
	\subsection{Deterministic Counterparts}
		List the test results of INFORMS presentation. State the fact that the fully stochastic makes great improvement over its deterministic counterparts.
\section{Stochastic Mixed Integer Program Extension}
\section{Conclusions} \label{sec:conclusions}
